Considering scale in multilayer animal social networks

### 2020-06-18 paper/manuscript.Rmd
revert to readRDS in manuscript
replace source variables for now
rm manuscript and supp from plan (for now)

drake::loadd(vars)

drake::loadd(data)
DT <- sub
setalloccol(DT)

drake::loadd(nobs)

timedefs <- fread('../data/supp-data/timecut-defs.csv')
```

@@

```{r lcres, fig.cap='(ref:lcres)'}
# knitr::include_graphics('../graphics/figure-lc.png')
drake::readd(lc_figure)
```

>>>>

source('../scripts/00-variables.R')

DT <- readRDS('../data/derived-data/01-sub-fogo-caribou.Rds')
nobs <- readRDS('../data/derived-data/05-number-of-observations.Rds')
timedefs <- fread('../data/supp-data/timecut-defs.csv')
```

@@

```{r lcres, fig.cap='(ref:lcres)'}
knitr::include_graphics('../graphics/figure-lc.png')
```
